Nail: A practical interface generator for data formats

### 2014-12-03 paper/login/design.tex
sync n*.bib

Just like C supports various constructs to build up types, such as structures and unions from pointers and
elemental types, Nail supports various \emph{combinators} to represent features of a file or protocol. We will present the features we used in implementing
DNS. A more complete reference can be found in Figure~\ref{fig:syntax}, with detailed rationale in~\cite{bangert:nail-osdi14}.

@@

Nail supports various forms of arrays. Line 40 shows how to parse a domain in a DNS packet with
\cc{many}, which keeps repeating the \cc{label} rule until it fails.  In the next section, we will
explain how to handle count fields, and our full paper~\cite{bangert:nail-osdi14} describes how to handle various array
representations (such as delimiters or non-empty arrays).

>>>>

Just like C supports various constructs to build up types, such as structures and unions from pointers and
elemental types, Nail supports various \emph{combinators} to represent features of a file or protocol. We will present the features we used in implementing
DNS. A more complete reference can be found in Figure~\ref{fig:syntax}, with detailed rationale in~\cite{bangert:nail}.

@@

Nail supports various forms of arrays. Line 40 shows how to parse a domain in a DNS packet with
\cc{many}, which keeps repeating the \cc{label} rule until it fails.  In the next section, we will
explain how to handle count fields, and our full paper~\cite{bangert:nail} describes how to handle various array
representations (such as delimiters or non-empty arrays).
